Viscous Transport in Eroding Porous Media

### 2019-06-12 docs/transport/erosion_transport.tex
do the result section in transport paper

We define the local tortuosity
$$\tau(y)=\frac{\lambda(y)}{d}$$ 
of the tracers at $y$ on the starting cross section
where $\lambda(y)$ is the trajectory length of the tracer at y 
and $d$ is the distance from the starting cross section to 
the endding starting cross section. }

@@

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the endding starting cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighbor tracers have been
seperated by the bodies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
In Fig.~\ref{fig:Eroding100vort}

In Fig.~\ref{fig:Eroding100tracer}

In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
and y in [-1,1]).

@@

}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256 $}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The trajectories of 200 tracers in the fluid with 100 bodies}
\end{center}
\end{figure}

>>>>

We define the local tortuosity
$$\tau(y)=\frac{\lambda(y)}{d}$$ 
of the tracers at $y$ on the starting cross section
where $\lambda(y)$ is the trajectory length of the tracer at y 
and $d$ is the distance from the starting cross section to 
the end cross section. }

@@

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighbor tracers have been
seperated by the bodies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256 $}
\end{center}
\end{figure}

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
In Fig.~\ref{fig:Eroding100vort}

To study the behavior of fluid in the porous media with multiple bodies, 
we release 1000 equal spreeding tracers from the 
starting cross section x = -1 and record their trajectories and velocities
until they arrive the end cross section x = 1. 
To understand the global action of fluid qualitatively, 
we only draw 200 historical trajectories from x = -1 to x = 1 
in Fig.~\ref{fig:Eroding100tracer}.

To measure the local behavior of fluid quantitatively, 
we use the velocities and local tortuosities at the starting cross section 
to analysis the interaction of fluid and bodies until the end cross section 
in Fig.~\ref{fig:Eroding100tort}.
In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the strating cross section.

@@

}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The historical trajectories of 
200 tracers released at x = -1 in the fluid with multiple bodies}
\end{center}
\end{figure}
